Tesseroids: forward modeling gravitational fields in spherical coordinates

### 2014-12-03 manuscript.tex
Added a little bit of text to accuracy section

The key controlling point of their algorithm is the ratio between
the smallest distance to the computation point and
the largest side length of the tesseroid.

The value of this ratio is used to decide whether a tesseroid will be divided
or not.

Thus, the value chosen for the minimum allowed value of this ratio determines
how many divisions are made.

Consequently, the value for the minimum distance-size ratio controls both the
accuracy of the integration and the computation time.

@@

However, there has been no further investigation into
the relationship between values of the minimum distance-size
ratio and the computation error.

It is also not clear whether the same relationship holds for the gravitational
attraction as well as for the gradient tensor components.

\subsection{$g_{zz}$ variability with computation height}

>>>>

The key controlling point of the adaptive discretization algorithm
is the distance-size ratio $D$ (equation~\ref{eq:condition}).

The value chosen for this ratio determines how many divisions are made.

$D$ controls both accuracy of the integration and the computation time.

@@

There has been no further investigation into
the relationship between values of the distance-size ratio and
the computation error.

It is also not clear whether the same value of $D$ used for the gravitational
attraction can be used for the gradient tensor components.

We need a reference value against which to compare the computed tesseroid effects.

The spherical shell is a convenient model with an analytical solution along
the polar axis.

\citep{Grombein2013} provides the equations for
the gravitational potential, attraction, and gravity gradient components
of a homogeneous spherical shell.
